DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-07 dryad/README.Rmd
adding to readme for dryad submission

	File 1 Name: Sanchez-Reyes_etal_2022_table_1.csv    
	File 1 Description:

	File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
	File 2 Description:

	File 3 Name: Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre    
	File 3 Description:

	File 4 Name: Sanchez-Reyes_etal_2022_figure_3_chronogram_small_example.tre    
	File 4 Description:

	File 6 Name: Sanchez-Reyes_etal_2022_figure_4A_topology_finches_mrca.tre    
	File 6: Description:

	File 7 Name: Sanchez-Reyes_etal_2022_figure_4B_topology_finches_ncbi.tre    
	File 7 Description:

	File 5 Name: Sanchez-Reyes_etal_2022_figure_5_chronogram_finches_example.tre    
	File 5 Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions.

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2013. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.pdf    
	File XXX Description: Results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
	File XXX Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
	File XXX Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
	File XXX Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
	File XXX Description:

@@

DATA-SPECIFIC INFORMATION FOR: Rye_2021_a_Cohort_IDs.xlsx

>>>>

	File 1 Name: Sanchez-Reyes_etal_2022_table_1.csv    
	File 1 Description: CSV (comma separated values) file containing results from the small example. Names and ages (in Million years) of nodes from source chronograms that have been congruified to nodes of the chosen tree topology.

	File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
	File 2 Description: CSV (comma separated values) file containing a summary of node age (in Million years) data from table S1.

	File 3 Name: Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre    
	File 3 Description: Newick version of chronogram from the mock example shown in Figure 1 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 4 Name: Sanchez-Reyes_etal_2022_figure_3_chronogram_small_example.tre    
	File 4 Description: Newick version of chronogram from the small example shown in Figure 3 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 6 Name: Sanchez-Reyes_etal_2022_figure_4A_topology_finches_mrca.tre    
	File 6: Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4A of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 7 Name: Sanchez-Reyes_etal_2022_figure_4B_topology_finches_ncbi.tre    
	File 7 Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4B of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 5 Name: Sanchez-Reyes_etal_2022_figure_5_chronogram_finches_example.tre    
	File 5 Description: Newick version of chronogram from the finch example shown in Figure 5 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
	File XXX Description: PDf file showing results of cross validation analysis of datelife's chronogram generating functions.

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2013. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
	File XXX Description: CSV (comma separated values) file

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
	File XXX Description: PDF file of

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
	File XXX Description: CSV (comma separated values) file

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
	File XXX Description: PDF file of r

@@

```{r}
files <- c()
text <- c()
for (file in 1:10) {

  text <- paste(text, 
                paste("DATA-SPECIFIC INFORMATION FOR:", file, "\\newline"))
}
text
```

`r text`
DATA-SPECIFIC INFORMATION FOR: Rye_2021_a_Cohort_IDs.xlsx

### 2022-07-07 manuscript/manuscript.Rmd
adding to readme for dryad submission

We illustrate the DateLife workflow using a family within the Passeriform birds encompassing the true finches, Fringillidae, as case study. The first example analyses 6 bird species and shows all steps of the workflow The second example is an analysis of 289 species in the family Fringillidae that are included in the NCBI taxonomy.
<!--We used `r cite_r("r-references.bib")` for all our analyses.-->

>>>>

We illustrate the DateLife workflow using a family within the Passeriform birds encompassing the true finches, Fringillidae, as case study. On a small example, we analyse 6 bird species, and show all steps of the workflow (Fig. \ref{fig:figure2}). As a second example, we analyse 289 species in the family Fringillidae that are included in the NCBI taxonomy (Fig. \ref{fig:fringillidages}).
<!--We used `r cite_r("r-references.bib")` for all our analyses.-->
